Consistent Polyhedral Surrogates via Embedding

### 2019-05-20 notes/jessie-proof-sketches.tex
Updated Corollary 1

  \jessie{Attempt 2: Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.  As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
  \jessie{Going to refresh my brain-- come back to this, but if the other proof is insufficient, this idea is chasing down the correct path.}
\end{proof}
\hrulefill
\begin{proof}[Property version]
  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
  To see our result, we specifically show that $L$ embeds $L|_\R$.

  Given the loss $L$, consider $\Gamma := \prop{L}$.
  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
\end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
  \jessie{Ready for a look over.}
\end{theorem}
\begin{proof}[Property version]
  Consider $\gamma := \prop{\ell}$, which is a finite property as $\dom(\ell)$ is finite.
  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
\end{proof}

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
  \jessie{Not happy with this, but not sure how to improve it.}
\end{corollary}
\begin{proof}[Property version]
	We just need to show that $2 \implies 1$.
	Consider the finite property $\gamma$ embedded by the discrete loss $\ell$. \jessie{Need a proof that $\ell$ is discrete?}
	By Theorem~\ref{thm:discrete-loss-poly-embeddable}, we know that there is a polyhedral loss $L$ that embeds $\ell$.
	Therefore, $\Gamma := \prop{L}$ embeds $\gamma$.
	Since $L$ elicits $\Gamma$, we can then see that $L|_\R$ elicits $\gamma' := \Gamma \cap \R$ by \jessie{COLT Lemma 11... hold up.  We need something else here.  This statement isn't quite true.}.
	Thus, $\gamma$ is elicitable by some relabeling of $L|_\R$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}

>>>>

  \jessie{Attempt 2: Since $L$ is polyhedral, it is the pointwise max of a finite set of affine functions.  As $\risk{L}$ is defined as the inf over a finite set of polyhedral functions, its epigraph is a subset of the expected loss for each report, and thus is still the finite intersection of closed halfspaces.}
\end{proof}
%\hrulefill
%\begin{proof}[Property version]
%  We know $L$ polyhedral implies $\risk{L}$ is polyhedral. \jessie{Does the above argument not work?  If it does, the other proof is shorter anyways.}
%  As before, construct, $\R = \{u_f\}_{f \in F}$, which is finite, as $F$ is finite. \jessie{We need the above statement to know that $F$ is finite, and therefore $\ell$ is discrete.}
%  To see our result, we specifically show that $L$ embeds $L|_\R$.
%  
%  Given the loss $L$, consider $\Gamma := \prop{L}$.
%  Revisiting the definition, it is apparent that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity.
%  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
%\end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
  \jessie{Ready for a look over.}
\end{theorem}
\begin{proof}[Property version]
  Given $\ell:\R \to \reals_+^\Y$, consider $\gamma := \prop{\ell}$, which is a finite property as $\R$ is finite.
  The result is a corollary of \jessie{COLT Theorem 35} Theorem~\ref{thm:general-duality-embedding}, where the polyhedral loss $L$ is as constructed in the proof.
\end{proof}
\hrulefill
%\begin{proof}[Non-property version]
%  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
%  It is sufficient to show the existence of a polyhedral loss $L$ such that $\risk{\ell} = \risk{L}$.
%  Consider that $\risk{\ell}$ is closed and concave, since the domain $\simplex$ is closed.
%  Now construct $L$ as in \jessie{DKR} Duchi et al.~\cite[Proposition 3]{duchi2010multiclass}, where $H = \risk{\ell}$.
%  Then we know that $\risk{L} = \risk{\ell}$ by their result, and thus $L$ embeds $\ell$ by Proposition~\ref{prop:embed-bayes-risks}.
%  Moreover, we can see that $L$ is polyhedral as it is a linear transformation of a polyhedral concave function $\risk{\ell}$.
%\end{proof}
%
%\hrule
%\hrulefill

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
  \jessie{Not happy with this, but not sure how to improve it.}
\end{corollary}
\begin{proof}[Property version]
  We just need to show that $2 \implies 1$.
  Suppose the loss $\ell$ embeds $\gamma:\simplex \toto \R$, and $\ell$ elicits some (possibly different) property $\gamma':\simplex \toto\R'$.
  If $\gamma$ and $\gamma'$ have the same level sets, then the elicitability of $\gamma'$ would imply that $\gamma$ is also elicitable, by $L(r) := \ell(\varphi(r))$.

  Since $\gamma'$ embeds $\gamma$, we know that there is an injection $\varphi$ such that $r \in\gamma(p) \iff \varphi(r) \in \gamma'(p)$.
  Therefore, for all $r \in \R$, we know that $\gamma_r = \gamma'_{\varphi(r)}$.
  (Consider that $p \in \gamma_r \implies p \in \gamma'_{\varphi(r)}$, and so $\gamma_r \subseteq \gamma'_{\varphi(r)}$, and vice versa.)
  Thus, the level sets are the same, and so $\gamma$ is elicitable by $L$ as described above.

\end{proof}
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\hrulefill
%\begin{proof}[Non-property version]
%  We trivially have $3\Rightarrow 2$.
%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
%  Finally, to see $2\Rightarrow 1$,
%\end{proof}
